EE454 Project 1 Report

### 2015-09-24 p1/report/latex/draft.tex
fix for adding layers

@@

>>>>

Image normalization takes each image and performs a linear scaling opera-
tion on each pixel in the image. The result is an image where each pixel (in
each channel) takes on a value in the range [-0.5 to 0.5].

\lstinputlisting[frame=single]{../../matlab/ImNorm.m}

\subsubsection{ReLU Layer}

Rectification takes an input image and thresholds all the negative values to 0.  This layer emulates neurons with a particular activation function.

\lstinputlisting[frame=single]{../../matlab/ReLU.m}

\subsubsection{Pooling Layer}

Pooling layers reduce variance in the image and reduce the overall size of the image by taking patches of the image and compressing that patch to a single pixel value.

\lstinputlisting[frame=single]{../../matlab/Maxpool.m}

\subsubsection{Convolutional Layer}

The convolution operation takes a set of filters and bias values determined from the CNN's training phase and applies them over an image.  The filter is applied with a convolution operator, and the bias is then added to every resultant pixel.

@@

\subsubsection{Fully-Connected Layer}

The fully-connected layer takes the output from the previous layer and maps it against every neuron in the network.  The output is a 1D vector of classifications (realized with soft max).

\lstinputlisting[frame=single]{../../matlab/FuCd.m}

\subsubsection{Soft Max Layer}

The soft max layer takes the output from the fully-connected layer and maps it as input to a probability space.  Each probability in the output of soft max corresponds to a classification likelihood.

\lstinputlisting[frame=single]{../../matlab/Softmax.m}
